A Logical Solution of the Linearity Challenge

### 2025-12-03 paper/Safety.lagda.tex
restored type safety

\section{Type Safety}
\label{sec:safety-agda}

\begin{code}[hide]
open import Data.Sum
open import Data.Product using (_,_)
open import Relation.Nullary using (¬_; contradiction)
open import Data.List.Base using ([]; _∷_; [_])

open import Type
open import Context
open import Process
open import Congruence
open import Reduction
open import DeadlockFreedom
\end{code}

@@

\begin{code}
data ReductionContext (Δ : Context) : Context → Set where
  hole   : ReductionContext Δ Δ
  cut-l  : ∀{Γ Γ₁ Γ₂ A B} (d : Dual A B) (p : Γ ≃ Γ₁ + Γ₂) →
           ReductionContext Δ (A ∷ Γ₁) → Process (B ∷ Γ₂) →
           ReductionContext Δ Γ
  cut-r  : ∀{Γ Γ₁ Γ₂ A B} (d : Dual A B) (p : Γ ≃ Γ₁ + Γ₂) →
           Process (A ∷ Γ₁) → ReductionContext Δ (B ∷ Γ₂) →
           ReductionContext Δ Γ
\end{code}

@@

\begin{code}
_⟦_⟧ : ∀{Γ Δ} → ReductionContext Δ Γ → Process Δ → Process Γ
hole ⟦ P ⟧           = P
cut-l d p 𝒞 Q ⟦ P ⟧  = cut d p (𝒞 ⟦ P ⟧) Q
cut-r d p Q 𝒞 ⟦ P ⟧  = cut d p Q (𝒞 ⟦ P ⟧)
\end{code}

>>>>

\subsection{Type Safety}
\label{sec:safety-agda}

\begin{code}[hide]
{-# OPTIONS --rewriting #-}
open import Data.List.Base using ([]; _∷_; [_])

open import Type
open import Context
open import Process
open import Congruence
open import DeadlockFreedom
\end{code}

@@

\begin{code}
data ReductionContext (Δ : Context) : Context → Set where
  hole   : ReductionContext Δ Δ
  cut-l  : ∀{Γ Γ₁ Γ₂ A} (p : Γ ≃ Γ₁ + Γ₂) →
           ReductionContext Δ (A ∷ Γ₁) → Process (dual A ∷ Γ₂) →
           ReductionContext Δ Γ
  cut-r  : ∀{Γ Γ₁ Γ₂ A} (p : Γ ≃ Γ₁ + Γ₂) →
           Process (A ∷ Γ₁) → ReductionContext Δ (dual A ∷ Γ₂) →
           ReductionContext Δ Γ
\end{code}

@@

\begin{code}
_⟦_⟧ : ∀{Γ Δ} → ReductionContext Δ Γ → Process Δ → Process Γ
hole ⟦ P ⟧         = P
cut-l p 𝒞 Q ⟦ P ⟧  = cut p (𝒞 ⟦ P ⟧) Q
cut-r p Q 𝒞 ⟦ P ⟧  = cut p Q (𝒞 ⟦ P ⟧)
\end{code}
